\section{Two Weapon Fighting}
\textbf{Minor Offense}

Fighting with two weapons has a long tradition. Assassins striking with a pair of daggers, pirates raiding their foes with a cutlass and flintlock, Cowboys with a six shooter in each hand, even battlemages who would swing a sword while raining fire on their foes all found value in a second weapon. 

\subsection*{Adaption}
This is a very general concept which can be used in many ways. Besides the obvious characters with 2 weapons, you can use it for someone who attacks with their offhand while doing something else with their main attention, such as casting spells, healing, summoning, etc. It can also be used with an unarmed character to represent them attacking extra fast, or an old 1-2. 
\begin{multicols*}{2}
\subsection*{First Facet\perk}
\textbf{Dual-Wield}: \emph{You have decided the best use of your other hand is to use a weapon.} You may wield 2 weapons at the same time. You may choose either weapon to make your major action with for the round, and all abilities from this track will use the other weapon, referred to as your offhand weapon.  Whenever you draw or switch weapons, you may draw or switch your offhand weapon as well.

\textbf{Offhand Blow} [W]:  You may attack an opponent at +1 to hit. This deals $3\times C\times Lvl$ damage on a hit.

\textbf{Offhand Strike}: You may use a surge with your offhand weapon. 

\subsection*{Second Facet}
\textbf{Combo Power}: You gain one of the following abilities each round, based on which types of weapon you are wielding. If you do not use your major action to attack with your weapon, you gain one of the other abilities based on your offhand weapon.
\begin{itemize}
\thing \textbf{Two Ranged Weapons} [W]: \emph{You can aim your weapons at two different targets effectively} As a minor action, when you attack with your major action, you may use it again; this cannot include targets that were targeted by the first action or other uses of this ability this round. You cannot use this with abilities that have the [S] tag. \textbf{Boost}: You may boost this major action.
\thing \textbf{Two Melee Weapons} [W]: \emph{You can create an opening for your attack.} As a minor action, your target takes a penalty against your major action, and [Vulnerability] to your attacks equal to your $C \times lvl$.
\thing \textbf{One Ranged and One Melee Weapon}: \emph{You can use your melee weapon to defend yourself while firing a ranged weapon.} You do not provoke reactions while firing a ranged weapon out of melee. If you hit with a melee attack, you can move the opponent 3 hexes away from you.
\thing \textbf{One Melee Weapon and a Non-Weapon Major} [W]: \emph{Your sword acts as a defense to ward off attackers while you work your magic} You do not provoke reactions from foes you target with your offhand weapon by using reckless abilities. Additionally, as a minor action you may strike everyone in melee range for $2\times C\times Lvl$ damage on a hit.
\thing \textbf{One Ranged Weapon and a Non-Weapon Major}: \emph{You force your opponents to dodge out of the way of your attacks} If you miss with your offhand attack, you may move its target 1 hex in any direction
\end{itemize}

\subsection*{Third Facet\perk}
\textbf{Dual Strike}: As a minor action, you may strike one target with your main weapon and another target with your offhand weapon, each at a +1 to hit, dealing $2\times C\times Lvl$ damage.

\textbf{Matched Pairs} : For each type of weapon you carry, you may carry an additional weapon of that type without counting against your max number of weapons.

\textbf{Doubled Reflexes}: You may take 1 Reaction with each weapon, if that weapon is capable of making reactions. You may still only take 1 reaction against any given action.

\textbf{Extreme Nimbleness}: If you wield 2 nimble weapons, you may avoid a reaction from moving even if you started in an enemy's melee range, as long as you were wielding both weapons at the start of your turn.

\subsection*{Fourth Facet}
\textbf{Deftness}: You gain one of the following abilities based on your offhand weapon:
\begin{itemize}
\thing \textbf{Melee}: Your offhand blow may also be a push, grapple, trip, or disarm attempt in addition to its damage.
\thing \textbf{Ranged}: The target of your off-hand blow is [Flat-footed]
\end{itemize}

\subsection*{Fifth Facet\perk}
\textbf{Rend}: \emph{The combined fury of your weapons leaves your opponents bleeding} Your offhand blow inflicts [Bleeding $C\times Lvl$] if it targets a creature targeted by your major action.

\textbf{Specialized Maneuvers}: Once per encounter, you may use one of the following abilities depending on your offhand weapon
\begin{itemize}
\thing \textbf{Corkscrew Dash} [W]: As a minor action while using a melee offhand weapon, you may dash 6 hexes, and strike every opponent within melee range of any hex you passed through. This deals $2\times C\times Lvl$ damage on a hit
\thing \textbf{Spray} [W]: As a minor action while wielding a ranged offhand weapon, you may strike 3 opponents. The same opponent may be targeted multiple times This deals $0.5 \times C \times Lvl$ damage per hit, and each target hit gains [Ongoing $C\times Lvl$]
\end{itemize}

\subsection*{Sixth Facet}
\textbf{X Defense}: \emph{You brace your weapon against your offhand weapon to steel yourself from oncoming attacks} As an immediate minor action, you may gain $2 \times C\times Lvl$ barrier hp. 

\subsection*{Seventh Facet\perk}
\textbf{Twinned Attack}: You focus both your weapons and attention to the task at hand
As a minor action, you may draw a offhand weapon that matches your main weapon without provoking, and gain 2 boosts to your major action and gain a rider that inflicts [Bleeding $C\times Lvl$] and [Slow 2] on a hit.
\end{multicols*}