\chapter{Features}
\begin{multicols*}{2}
Characters gain two Features at level 1, and an additional single feature at 3, 6, 9, 12, 15, and 18, for a total of eight features.

Features are abilities that are useful tactically or combatively. By default, they can be taken only once. Select features can be taken more than once, and have greater effect according to the feature.

\subsection*{Monster Tactical Abilities}
At level 1 only, you can spend your two starting features to get a single monster tactical ability to help represent a more capable character concept, such as a powerful race. (See Monster Generation)

\subsection*{Features}
\subsubsection{Ancestral Weapon}
\emph{You have a deep bond with your weapon, allowing you to unlock more power.}

\textbf{Prerequisite}: A bound item with a weapon chosen

You may pick a second magic weapon; instead of gaining a second magic weapon, your bound weapon will have the effect of this in addition to its existing effects

\subsubsection{Armory}
You can carry 2 additional weapons.

\subsubsection{Artificier}
\emph{You’ve got a keen eye for the magically potent leftovers of a fight.}

After an encounter, you get one set of Artifact Scrap; either in the form of loot from your opponents, the detritus left after a fight, or materials from the monsters themselves.

You can use five sets of Artifact Scrap to create a single Depletable Artifact (see Items).

\subsubsection{Assisted Leap}
You serve as an excellent base to propel someone else to new heights. An ally can jump off you or be thrown by you to 2 higher than they started as a Jump as part of their movement while adjacent to you. This includes vertical adjacency.

You can select this feature additional times; each selection increases the height by 2.

\subsubsection{Benefactor}
Whenever you would be healed by any effect, you may forgo that healing to heal an ally within 12 hexes the same amount.

\subsubsection{Blinker}
Once per encounter, you can exchange MP to teleport hexes equal to the amount of MP you’ve exchanged.

You can select this feature a second time. If you do, you may use this ability any number of times per encounter.

\subsubsection{Bloody Cleave}
When you would gain bloodlust, you may instead make an immediate weapon attack at -2 to hit that deals twice the amount of bloodlust in damage.

\subsubsection{Bound Item}
Pick one Major Item as a bonus item. You gain and always have the benefit of this item.

\subsubsection{Breakneck Pace}
You gain 3 additional movement points per turn.

\subsubsection{Careful Advancement}
You can spend double the movement points to move through an afflicted hex without triggering its effect.

\subsubsection{Cause Overreach}
Once per encounter, while you are flanked, if one of the creatures flanking you misses you with a pool attack or a strike, you may choose to have that attack hit you. If you do, another creature flanking also is hit by that attack.

\subsubsection{Combat Mastery}
Twice per encounter, you may use a combat maneuver, but no more than once per round.\\
You can select this feature one additional time. If you do, you gain another two uses.

\subsubsection{Combat Toss}
Once per encounter, you may make an attack roll against an adjacent creature. If you hit, that enemy is pushed 3 hexes away from you.

\subsubsection{Counterflip}
Twice per encounter, when an enemy misses you with a melee attack, you may immediately use the Trip combat maneuver against them.

You can select this feature an additional time. If you do, you may use this ability any number of times per encounter, but only once per round.

\subsubsection{Countershove}
Twice per encounter, when an enemy misses you with a melee attack, you may immediately use the Push combat maneuver against them.

You can select this feature an additional time. If you do, you may use this ability any number of times per encounter, but only once per round.

\subsubsection{Cowboy Style}
Once per encounter, you may use the disarm combat maneuver with a ranged weapon

\subsubsection{Defensive Fighter}
When you take a major action, you may choose to take a penalty to that action. If you do, You become [Guarded 1]. You cannot use this if the action would already have 2 penalties

\subsubsection{Desperate Dash}
You may gain up to 6 extra movement points this round, but the round after you will lose the same number of movement points. 

\subsubsection{Elemental Nova}
Prerequisite: An ability that delivers an [Energy condition].

Pick one ability you possess from any track or \facet that inflicts an elemental condition. When you would inflict an [Energy condition] with the chosen ability, you may also inflict that elemental condition on each creature adjacent to that creature. You may reselect the ability associated with this feature when you gain a level.

\subsubsection{Evade Notice}
Once per encounter, you may lower your target priority for 1 [Round]. You cannot be attacked if there is a higher priority target available.

\subsubsection{Expanded Knowledge}
You may ask 2 additional questions about your enemies during an encounter as if your Brain attribute was 2 higher.

You may take this feature an additional time. If you do, you may instead ask 4 additional questions.

\subsubsection{Extended Blitz}
Once per Encounter, when you would make a melee attack, you may choose to make that attack a ranged attack against any creature within 6 hexes. This doesn’t provoke.

\subsubsection{Falling Dominoes}
If you would move an adjacent enemy three or more hexes, if they are also adjacent to another enemy, you may instead knock both those enemies [prone].

\subsubsection{Familiar}
You gain the companionship of a small creature with 1 tactical ability from the monster tactical ability list. It has a speed of 6 and your AC, moves on your turn, and can share hexes with other creatures. You may draw LoS from its hex. It has $2\times C\times Lvl$ HP and is [Bonded] to you, but it is immune to AoEs while it is adjacent to an ally. It may [mount] you or an ally. If it is killed, you may replace it between encounters.

You may select this feature multiple times. Each time after the first, instead, you may increase the HP of your familiar by up to $2\times C\times Lvl$, and it gains an additional ability from the monster tactical ability.

\subsubsection{Flares \R }
\emph{Your attacks are bright! As an autohit rider, your attacks may add [Light] to the hex they target for the encounter.}

Once per encounter, you may gain a rider that inflicts [Blinded 6] on a hit.

You may select this feature multiple times. Each time you do, you may use the once per encounter component of this feature an additional time.

\subsubsection{Intersector}
If an ally adjacent to you is targeted by an ability that does not also target you, you may move into the nearest hex in the abilities range and have it target you instead.

\subsubsection{Improved Charge}
You can charge 2 extra hexes and ignore difficult terrain while charging or running.

\subsubsection{Long Draw}
Once per encounter, for two rounds, your melee reach is extended by 1 hex.

\subsubsection{Major Telekinesis \R }
Once per round, you can Fforce Move a creature within 12 hexes other than you one hex by spending one movement point.

\subsubsection{Minor Telekinesis}
You may begin wielding any non-wielded weapon within 6 hexes of you with 1 mp, or pull a similarly sized item to you.

\subsubsection{Nimble feet}
Once per encounter, you may dash 2 hexes.

You may select this feature one additional time. If you do, you may use this twice per encounter instead of once.

\subsubsection{Paranoid}
They will call you paranoid for taking this feature until you get ambushed, and then they’ll simply call you prepared.
You cannot be ambushed, and can always act in surprise rounds.

\subsubsection{Piggyback}
Whenever an ally is in a hex adjacent to you, you may spend a movement point to put that ally on your back or that ally may spend a movement point to hop on your back. That ally becomes [Mounted], and you are the [Mount].

\subsubsection{Powerdive}
\textbf{Prerequisite}: Flier.

Once per encounter, if you attack an enemy after moving downwards, subtract your current height from the  highest height  you had this round. You may push the enemy 1 hex for every 3 this difference is.

\subsubsection{Prioritizer \R }
Once per encounter, when making a ranged attack, you may ignore target priority.

\subsubsection{Protectors Pass}
You can activate this ability once per encounter. When you activate this ability, for the rest of the encounter, whenever an enemy enters an adjacent hex to you, you may make an attack roll against that enemy. If you hit, that enemy becomes [Stopped] for the remainder of their turn. This ability ends if you leave the hex you initiated this ability on for any reason.

\subsubsection{Recall Point}
Once per encounter, at any point in an encounter, you may set a hex you’re on as a Recall Point.

Unlimited times an encounter, on your turn, you may spend your remaining MP to return to that hex as a [warp] teleport.

\subsubsection{Reckless Strike}
When you make a melee attack, you may also use a surge. If you do, your opponent may use a surge against you first.

\subsubsection{Relocaport}
\textbf{Prerequisites}: Having access to a Teleport ability.

You can now teleport an enemy within melee range as if it was targeted by a teleport ability you possess, to a location within the teleport abilities targeting, or range 12, whichever is lower. This counts as a use of that teleport ability.

When you would use an ability that allows you to teleport an ally, you may teleport an enemy as if they were your ally. That enemy may make a defense roll. If the defense roll succeeds, they may choose the destination of the teleport, otherwise you choose. The radius of the teleport is as defined by the base ability, which is still treated as used when you use this ability.

\subsubsection{Restoration}
Once per encounter, when you target an ally with an ability, you may cure one [restorable; lesser] effect.

\subsubsection{Ricochet Shot}
Once per encounter, when you use a ranged ability that does not possess the [S] tag against an enemy, you may take a penalty on that attack. If you do, you may also make a rider attack at a +1 bonus. If the rider attack hits, you may use that attack again, but you cannot target the same creature. The second attack still has a penalty.

\subsubsection{Running Cleave}
You can dash three hex for free after reducing any target to 0 HP.

You may take this feature any number of times. Each time after the first, you increase the distance that you dash by 3 hexes.

\subsubsection{Saint}
You can walk on most liquids as if they were solids. This includes water.

\subsubsection{Scanner Array}
You gain [Scanner] out to range 12. Optionally, you may type your ability as [ground] or [mental] to add +12 to the base range.

You may take this feature any number of times. Each time you do, you may either increase the range by 12, or remove the [Ground] or [Mental] tag.

\subsubsection{Selective Shockwave \R }
\textbf{Prerequisite}: an AoE ability

When you use an AoE, you may have one ally in the area [Dash 2] before it takes effect

\subsubsection{Shadow Shot}
Once per encounter, choose a creature adjacent to a hex that you have line of sight and line of effect to. You have line of sight and line of effect to that creature for one round.

\subsubsection{Sideswiper}
You may use two reactive strikes per round.

\subsubsection{Signal Flashlight}
Each round, you may choose an enemy. Everyone has line of sight to that enemy for the round, but everyone also has line of sight to you, and you cannot benefit from stealth.

\subsubsection{Skedaddle}
Once per encounter, gain 6 additional movement points for one round.

\subsubsection{Smoky Tracer}
Once per encounter, you can allow a ranged ability you possess to leave a [cloudy] smoke trail along it’s line of effect that lasts for 1 round. If that ranged ability would have multiple lines of effect, pick only one.

You may take this feature any number of times. Each time you do, you gain an additional use per encounter.

\subsubsection{Spellguard}
\textbf{Prerequisites}: An ability that provokes Reactive Strike

Pick one ability you possess from any Aspect or Facet that is tagged as [Reckless] or [Reckless Melee] (See the Aspects chapter). This ability no longer has that tag. If you gain a new Facet in the Aspect from the ability you select, you can choose to have Spellguard remove the [R] pr [Rm] tag from that ability instead as a permanent switch you choose every time you gain a new Facet in that Aspect.

You may take this feature any number of times. Each time you do, you may select an additional ability.

\subsubsection{Spread the Love \R }
Once per encounter, you can transfer any boosts you have to an ally within 12 hexes.

\subsubsection{Surprising Blow}
You may switch weapons without provoking.  Once per encounter, you may gain a rider that inflicts [Off Balance] on a hit.

You can select this feat any number of times. Each time you do after the first, you gain an additional use of the Rider per encounter.

\subsubsection{Take the Grenade}
When you would be affected by an enemy’s ability that also affects your allies, you may become subject to that ability an additional time. If you do, your allies are unaffected by that ability.

\subsubsection{Telepathic Extension}
You can extend your senses across telepathic sources to draw Line of Sight from any ally in telepathic communication with the Telepathic Hub that you are connected to.

\subsubsection{Telepathic Hub}
You can communicate telepathically with all allies within range $3\times lvl$.

\subsubsection{Trackformer}
Select two tracks that are the same action cost. (for example, sniper and human shield. Both are sized Major.) One of these tracks must be a track you already possess. This is a permanent choice. Out of combat and at the start of a combat encounter, you may switch between these tracks. This can be the same track selected twice by this feature with different choices made within that track in each instance, such as Extraplanar Pacts, selecting all demon options on one side and all angel options on the other. You only gain a Perk Point from a track per \facet if both aspects would give a Perk Point at that \facet.

\subsubsection{Vertiginous Impact}
You may spend 1 mp to force the target of your attack 1 hex away from you. A successful defense roll negates this movement.
Once per encounter, you may gain a rider that inflicts [Dizzy 2] on a hit.

You can select this feat any number of times. Each time you do after the first, you gain an additional use of the Rider per encounter.

\subsubsection{Wallwalker}
You can walk on non-floor solids as if they were the floor.

\subsubsection{Warpport}
\textbf{Prerequisites}: Having access to a Teleport ability, level 15

Once per encounter, you can make a teleport you initiate a [warp] effect.

You can select this feat any number of times. Each time you do after the first, you gain an additional use of this ability.

\subsubsection{Weapon Implant}
Choose one of your weapons. That weapon becomes a natural weapon.

\subsubsection{Wetworker}
While in nondamaging liquids, you no longer spend twice the MP when moving in them.

\subsubsection{Zugzwang}
\emph{You force your opponent's move, even when it would be disadvantageous.}

Once per round, when opponent starts their turn in [Melee] range of you, you may make a strike at them. If it hits, they must spend at least 1 movement point to move during this turn, if able. This first hex of movement will not provoke reactive strikes and they cannot return to that hex on this turn.

\end{multicols*}