\chapter{Monster Abilities and Creation}

Every intrepid adventurer needs a dangerous, meaty wall of flesh to stand between them and their heroic deeds. Preferably interesting ones with exotic powers and strange, deadly abilities, so when they re-tell the tale later it’s much more interesting than that \emph{other} adventurers stories about how they felled a horde of weak, puny monsters.


Here’s a quick, powerful ruleset to build them.

\subsubsection{Monster Generation Step-by-Step}
\begin{enumerate}
\item Assign a level, and then use the base stats by level from the Basic Stats Table.
\item Assign attributes, with the following array: 4, 2, 1, 0.
\begin{enumerate}
\item \textbf{Brawn}: Each point of brawn lets you make a combat maneuver as a free action once per encounter.
\item \textbf{Agility}: Each point of agility lets you increase your speed by two for one round once per encounter.
\item \textbf{Brains}: Each point of brains lets the monster pick an additional primary major, secondary major or minor ability.
\item \textbf{Mojo}: Each point of mojo lets you raise or lower your target priority by one for one enemy for round. If you raise it, you can take a surge on someone who violates this target priority. If you lower it, you gain a 25\% dodge chance against attacks that violate this target priority.
\end{enumerate}
\item Choose between:
\begin{enumerate}
\item \textbf{Wield Weapons}: The monster possesses three weapons, and can switch between them, similar to a PC.
\item \textbf{Natural Weapon}: The monster possesses a single natural weapon, and cannot be disarmed.
\end{enumerate}
\item Choose two major abilities. A monster at least one primary major ability, this can be by having either a primary major abilities and a secondary major abilities, or having two primary major abilities. Primary major abilities are suitable for a backbone ability, while secondary major abilities are intended for more occasional use, or as a backup if they can't use their primary major for whatever reason. It is strongly recommended that each monster have something it can use at range and in melee.
\item Choose one minor ability. In addition to this, all monsters gain the Rest minor ability for free.
\item If the monster has a Brain attribue higher than 0, choose an additional primary major ability, secondary major ability or minor ability for each point that the monster has in brains.
\item Define Surges.
\begin{enumerate}
\item If the creature has no abilities that grant a surge, they can use the basic surge.
\item If the creature has multiple abilities that grant surges, they can choose between all of their available surges when making a surge attack.
\item Abilities with the [surge] tag can be used as a surge ability. If the minor ability attaches a rider, the target of the surge is targeted by the rider.
\end{enumerate}
\item Choose a passive ability.
\item Determine tactical abilities.
\begin{enumerate}
\item Creatures of levels 1 to 4 gain one tactical ability. Creatures of levels 5 to 10 gain two tactical abilities. Creatures of levels 11 to 16 get three tactical abilities. Creatures of levels 17 or higher gain four tactical abilities.
\item A creature may swap a tactical ability for the native ability if the situation warrants it.
\item A monster with one aspect gets half the number of tactical abilities, rounded down. A monster with two or more aspects gains no tactical abilities.
\end{enumerate}
\end{enumerate}

\begin{figure}[h]
\center
\begin{tabular}{c c}
\begin{tabular}{p{0.5\textwidth}}
\textbf{Basic Surge}: The creature has a basic surge unless otherwise specified by a major action.\\ 

It is at normal accuracy and does damage according to Row S. 
\end{tabular} &

\begin{tabular}{|c||c|c|c|c|c|}
\hline 
\textbf{Lvl} & 1 & 2 & 3 & 4 & 5 \\
\hline
\textbf{S} & 10 & 21 & 31 & 42 & 70 \\
\hline
\multicolumn{6}{c}{ }\\
\hline
\textbf{Lvl} & 6 & 7 & 8 & 9 & 10 \\
\hline
\textbf{S} & 84 & 98 & 112 & 126 & 140 \\
\hline
\multicolumn{6}{c}{ }\\
\hline
\textbf{Lvl} & 11 & 12 & 13 & 14 & 15 \\
\hline
\textbf{S} & 192 & 210 & 227 & 245 & 262 \\
\hline
\multicolumn{6}{c}{ }\\
\hline
\textbf{Lvl} & 16 & 17 & 18 & 19 & 20 \\
\hline
\textbf{S} & 280 & 357 & 378 & 399 & 420 \\
\hline
\end{tabular}
\end{tabular}
\end{figure}

\begin{figure}[h]
\center
\textbf{Basic Stats Table}\\
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
\hline 
\textbf{Lvl} & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\
\hline
\textbf{HP} & 48 & 96 & 144 & 192 & 320 & 384 & 448 & 512 & 576 & 640 \\
\hline
\textbf{AR} & +2 & +3 & +4 & +5 & +6 & +7 & +8 & +9 & +10 & +11 \\
\hline
\textbf{DV} & 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 & 19 & 20 \\
\hline
\textbf{AV} & 13 & 14 & 15 & 16 & 17 & 18 & 19 & 20 & 21 & 22 \\
\hline
\textbf{AR} & +1 & +2 & +3 & +4 & +5 & +6 & +7 & +8 & +9 & +10\\
\hline
\multicolumn{11}{c}{ } \\
\hline 
\textbf{Lvl} & 11 & 12 & 13 & 14 & 15 & 16 & 17 & 18 & 19 & 20 \\
\hline
\textbf{HP} & 880 & 960 & 1040 & 1120 & 1200 & 1280 & 1632 & 1728 & 1824 & 1920 \\
\hline
\textbf{AR} & +12 & +13 & +14 & +15 & +16 & +17 & +18 & +19 & +20 & +21 \\
\hline
\textbf{DV} & 21 & 22 & 23 & 24 & 25 & 26 & 27 & 28 & 29 & 30 \\
\hline
\textbf{AV} & 23 & 24 & 25 & 26 & 27 & 28 & 29 & 30 & 31 & 32 \\
\hline
\textbf{AR} & +11 & +12 & +13 & +14 & +15 & +16 & +17 & +18 & +19 & +20\\
\hline
\end{tabular}
\end{figure}

\subsection*{Monster Abilities}
\subsubsection{Primary Major Abilities}
\begin{tabular}{|c c c c c|}
\hline
\multicolumn{5}{|c|}{\cellcolor{gray}\textbf{Offense}} \\
\hline
Auto-Damage & Basic Attack & Blaster & Binding$^\ast $  & Disorienting Blows \\
 & & & & \\
Flurry$^\ast $  & Improved Grab & Precise$^\ast $  & Rend$^\ast $  & Slug$^\ast $  \\
 & & & & \\
 & Swarm & Touch of Death & Tripper$^\ast $ & \\
\hline
\multicolumn{5}{c}{ }\\
\hline
\multicolumn{5}{|c|}{\cellcolor{gray}\textbf{Defense}} \\
\hline
 & Drain$^\ast $ & Leech$^\ast $ & Vampiric$^\ast $ & \\
\hline
\multicolumn{5}{c}{ }\\
\hline
\multicolumn{5}{|c|}{\cellcolor{gray}\textbf{Other - (V)aried and (M)ixed}} \\
\hline
 & Hampering$^\ast $ (M) & & Major Aspect$^\ast $ (V)  & \\
\hline
\end{tabular}



