\section{Battle Bonds}
\textbf{Passive Varied}

You are your partner can face any foe, as long as you’re together.

\subsection*{Adaption}
This track can be used to represent the power of true love, an oath to protect your partner, or linked twins. 

\emph{Sidebar: Some of the abilities are shared by both, such as Share HP and it’s effects, and others are usable only by the character with this track, not the partner - the one with this track has a higher investment in the partnership and has more abilities relating to that.}

\begin{multicols*}{2}
\subsection*{First \Facet\perk}
\textbf{Thick and Thin}: When you gain this \facet{}, choose an ally. That ally becomes your partner. You are not their partner unless they also possess this \facet and designate you as their partner.

\textbf{Right Behind You!}: Twice per encounter, you can raise or lower the target priority of your partner by 1. If an enemy violates this target priority, they gain [Vulnerable $C\times lvl$] to the next attack made by you or your partner.

\textbf{Partnered Benefits}: Choose one of the following. You gain that ability. This choice is permanent.
\begin{itemize}
\thing \textbf{Shared Skills}: You begin each encounter with four [Partner] tokens. Once per round, you may spend a [Partner] token to use a surge, or to allow your partner to use a surge. When using this ability, you may use your ally's surge ability, and they may use yours. This can be done during either your turn or your partner's turn. Additionally, you may choose a [Vengeance] ability. \textbf{Refresh}: As a refresh, gain an additional [Partner] token. You may use this ability an additional time during your next turn.
\thing \textbf{Duo}: You begin each encounter with four [Partner] tokens. Once per round, you may spend a [Partner] token to give you and your ally a boost.  Additionally, you may choose a [Vengeance] ability. \textbf{Refresh}: As a refresh, gain an additional [Partner] token. You may use this ability an additional time during your next turn.
\thing \textbf{Warmth}: Twice per encounter, you may heal your partner by $4\times C\times Lvl$, or your ally may heal you by $4\times C\times Lvl$. Excess healing becomes Temporary Hit Points. You do not gain a [Vengeance] ability. \textbf{Refresh}: As a refresh, you may heal yourself or your partner by $2\times C\times Lvl$. Excess healing becomes Temporary Hit Points.
\thing \textbf{Shared Stoneskin}: At the beginning of each encounter, you and your partner each gain $4\times C\times Lvl$ resistance. \textbf{Refresh}: As a refresh, you may gain $2\times C\times Lvl$ resistance, or you may have your ally gain $2\times C\times Lvl$ resistance.
\end{itemize}

\textbf{Vengeance}: If you have the Shared Skills ability or the Duo ability, choose one of the following. You gain that ability. This choice is permanent.
\begin{itemize}
\thing \textbf{Retribution}: While your partner is [Wounded], you may spend a [Partner] token to use a surge. You may use your partner's surge ability instead of your own. While you are [Wounded], your partner may spend one of your [Partner] tokens to use a surge. They may use one of your surge abilities instead of their own.
\thing \textbf{Fury}: While your partner is [Wounded], you may spend a [Partner] token to become [Energized $2\times C\times Lvl$]. While you are [Wounded], your partner may spend a [Partner] token to become [Energized $2\times C\times Lvl$].
\end{itemize} 
\subsection*{Second \Facet\perk}
\textbf{Share HP}: Once per turn, you may take an amount of damage not exceeding a quarter of your current HP. Your partner heals an amount equal to the damage you took this way. Once per turn, your partner may take an amount of damage not exceeding a quarter of their current HP. You heal an amount equal to the damage they took this way.

\textbf{Lockstep}: You and your partner may spend double the movement points when entering a hex. If either of you do this, the other may move one hex in the same direction. Additionally, choose either Dizzy, Stop, Slow or Prone. This choice is permanent While you are within radius 3 of your partner, you and your partner are both immune to the chosen condition, as well as forced movement.

\subsection*{Third \Facet\perk}
\textbf{Furious Vengeance}: You only gain this ability if you possess either Retribution or Fury. Once per round, while your partner is [Wounded], when you would make an attack, that attack gains a rider. Once per round, while you are [Wounded], when your partner would make an attack, that attack gains a rider. In both circumstances, the rider automatically hits and either inflicts [Prone] or pushes the enemy one hex.

Choose one of the following:
\begin{itemize}
\thing \textbf{Pull It Together}: When you or our partner uses Share HP, choose a [Restorable; Lesser] condition affecting the creature healed through Share HP. End that condition.
\thing \textbf{Scissor}: When you deal damage to an enemy, if your partner has also dealt damage to that enemy since the beginning of your last turn, that enemy begins [Bleeding $C\times Lvl$]. When your partner deals damage to an enemy, if you also dealt damage to that enemy since the beginning of your partner's last turn, that enemy begins [Bleeding].
\thing \textbf{Take My Hand}: If you have a movement type (swim, fly, burrow, jump, teleport) you can allow your partner to also have it while adjacent to them.
\end{itemize}

\subsection*{Fourth \Facet}
\textbf{Anything for you}: Once per round, when your partner would take damage, you may choose to take that damage instead. This counts as a use of Share HP.

\textbf{Perfect Communication}: You and your partner can always communicate perfectly and, if willed, without being overheard, as long as you have line of sight to each other. This can be telepathy, hand signs, code phrases, or other.

\textbf{Shared Senses}: You and your partner may draw Line of Sight as though you were in either your hex or your allies hex.

\subsection*{Fifth \Facet}
Choose one:
\begin{itemize}
\thing \textbf{Shooting Star} Once per encounter, you may teleport to any hex within range 3 of your partner, or your partner may teleport to a hex within range 3 of you. Teleportation made as part of this ability has the [Warp] descriptor.
\thing \textbf{Fearless}: While you and your partner are within radius 6 of each other, you and your partner are both immune to fear.
\end{itemize}

\subsection*{Sixth \Facet}
\textbf{Riotous Vengeance}: If you or your partner is wounded and you possess a Vengeance ability, attacks made by you or your partner gain one of the following riders.
\begin{itemize}
\thing \textbf{Push}: This rider automatically hits. A creature hit by this rider is moved two hexes.
\thing \textbf{Trip}: This rider automatically hits. A creature hit by this rider becomes [Prone]. At the beginning of their next turn, they become Off Balance.
\end{itemize}

\textbf{Not Alone}: Once per encounter, when you are adjacent to your partner, you may use Share HP on them while they are [Wounded]. When used this way, if your partner's HP increases to above 0, they stop being [Wounded].

\subsection*{Seventh \Facet\perk}
\textbf{Together Forever}: You may spend a movement point to give your partner a movement point. Your partner may spend a movement point to give you a movement point. You and your partner may both move during both your turn and your partner's turn.

Choose one:
\begin{itemize}
\thing \textbf{Tag Team} Once per round, during your turn, you may teleport to your partner's hex. When you do, your partner teleports to your hex without provoking reactions. Once per round, during your partner's turn, your partner may teleport to your hex. When your partner does this, you teleport to your partner's hex. All movement made with this ability has the [Warp] descriptor.
\thing \textbf{Harmonic Movement}: When you or your ally would take their turn, you may both take your turn simultaneously.
\end{itemize}
\end{multicols*}
