\section{Lawbearer}
\textbf{Minor Mixed}

You set the law and you enforce it.

\subsection*{Adaption}
This track can be used to represent \emph{??}.

\begin{multicols*}{2}
\subsection*{First \Facet\perk}
\textbf{Set Law}: As a minor action, choose an enemy within 12 hexes of you and a law. During their next turn, that enemy may choose to follow the limitations of the chosen law. If they do not, they become a [Lawbreaker]. The following is a list of available laws. You may treat [Lawbreakers] as having a target priority one stage higher.
\begin{itemize}
\thing \textbf{Minor Denial}: The chosen enemy cannot take minor actions.
\thing \textbf{Off Limits}: Choose 3 hexes, plus one additional hex for every level you possess. The chosen hexes cannot be adjacent to the adjacent creature. The chosen creature cannot enter the chosen hexes, and cannot draw line of sight through those hexes.
\thing \textbf{Mirror}: Choose a [Restorable; Greater] and a [Restorable; Lesser] effect currently you. The chosen creature gains those effects.
\end{itemize}

\textbf{Punish Lawbreakers}: As a minor action, you can use two surges against a [Lawbreaker]. That creature is no longer a [Lawbreaker].

\textbf{Shackle Lawbreaker}: As a minor action, choose a [Lawbreaker] within 12 hexes of you. That creature stops being a [Lawbreaker] and gains shackles. The shackles are an [Equipped] effect, and have $2\times C\times Lvl$ HP, but are not [Bonded]. The shackles disappear after two turns. At the end of each of your turns, while the shackles last, the shackled creature becomes [Weakened $2 \times C\times Lvl$].

\textbf{Debt Repaid}: When a [Lawbreaker] becomes [Wounded], you gain a refresh.

\subsection*{Second \Facet\perk}
\textbf{The Watchful Eye of the Law}: You gain [Scanner 12], however, all creatures gain immunity to this. Whenever a creature becomes a [Lawbreaker], that creature loses this immunity for the rest of the encounter.


\subsection*{Third \Facet\perk}
\textbf{Escape Fee}: For each enemy, once per encounter, when that enemy would stop being a [Lawbreaker], you may choose a [Restorable; Lesser] effect currently affecting you. You lose that condition, and that enemy gains that condition with the remaining duration.
\textbf{Strict Guidelines}: Once per encounter, as a minor action, choose an enemy. That enemy may immediately make a triggered strike or take a minor action with all decisions made by you. If they do not, they become a [Lawbreaker].

\subsection*{Fourth \Facet\perk}
\textbf{Criminal Record}: Whenever a creature becomes a [Lawbreaker], if it is not the first time in the encounter that it has become a [Lawbreaker], it becomes [Stopped] for one round.

\subsection*{Fifth \Facet\perk}
\textbf{Police Brutality}: Once per encounter, choose an enemy within 12 hexes. You may spend a minor action to have that enemy become [Unguarded 2] and their target priority increases by two stages. That enemy may choose to negate this by becoming a [Lawbreaker].

\subsection*{Sixth \Facet\perk}
\textbf{Leniency}: As an immediate minor action, when an enemy would become a [Lawbreaker], you may choose for that enemy to not become a [Lawbreaker]. If you do, you may take an additional major action during your next turn.

\subsection*{Seventh \Facet\perk}
\textbf{Profiling}: Once per encounter, as a minor action, choose an enemy within 12 hexes. That enemy becomes a [Lawbreaker].

\end{multicols*}