\section{Rage}
\textbf{Passive Offense}

Characters with the rage aspect have learnt to master their rage and use it to annihilate their enemies.

\subsection*{Adaption}
Oddly enough, in some ways, this track rewards a sense of ``honour''. You attack people who attacked you first. As a result, this can be used to represent an honourable fighter.



\begin{multicols*}{2}
\subsection*{First \Facet\perk}
\textbf{Don't Tick Me Off}: \emph{You get angry at the slightest grievance.} Whenever an enemy tries to target you with an offensive ability or you make a reactive strike against an enemy, you may treat that enemy as a [Victim] until the end of your next turn. If, at the beginning of your turn, there are no [Victims] within 12 hexes, the nearest enemy to you becomes a [Victim] until the end of your turn. You may treat [Victims] as though their target priority was one stage higher.

\textbf{Muscle Drain}: You begin each encounter with no muscle drain. Once per round, if you have less than four muscle drain, you can use one of the following abilities. When you do, you gain a point of muscle drain after using the ability.
\begin{itemize}
\thing \textbf{Angry Attack}: When you damage a [Victim], you may increase the damage by $2 \times C \times lvl$ and make a rider attack. If the rider attack hits, the [Victim] is moved two hexes away from you. This distance is reduced by one for every two points of muscle drain you have. If you damaged the enemy with a melee weapon, that [Victim] is instead moved four hexes away from you. This distance is instead reduced by one for every point of muscle drain you have. 
\thing \textbf{Friendly Fury}: When you use an action that affects one or more allies, choose one of the affected allies, and an enemy who is currently a [Victim]. The next time that the chosen ally deals damage to that enemy, they may increase the damage by $2 \times C \times Lvl$ and make a rider attack. If the rider attack hits, the [Victim] is moved two hexes away from the ally. This distance is reduced by one for every two points of muscle drain you possess. If this ability was triggered by damage with a melee weapon, the enemy is instead moved four hexes away from the ally. This distance is reduced by one hex for every point of muscle drain you have.
\end{itemize}

\textbf{Refresh}: As a refresh, you may lose one point of muscle drain. If you have no muscle drain, prevent the next point of muscle drain you would gain. Additionally, you may use Angry or Friendly Fury an additional time during either your current or next turn.

\textbf{Final Ferocity}: When you would become [Wounded], you may use four surges against the last enemy to deal you damage. For each point of muscle drain you have, you use one less surge with this ability. You may switch your weapon before each surge. When you do this, you gain one point of muscle drain for each surge you used.

\subsection*{Second \Facet\perk}
\textbf{No Escape}: \emph{When you're ticked off, there is no escape from your wrath.} For each [Victim], the first time each round that that [Victim] would move away, you may dash four hexes and use a surge against them. The distance you can dash is reduced by one hex for each point of muscle drain you have. If a creature moves away from you, becomes a [Victim], and then moves away from you again, that still triggers this ability. Enemies are aware of this effect, even before any enemy becomes a [Victim].

\subsection*{Third \Facet\perk}
\textbf{Fear the Beast}: \emph{If someone hasn't drawn your ire, it is in their best interest to keep it that way.} Whenever an enemy who is not a [Victim] moves into or our of a hex adjacent to you, that enemy may become [Slow X], where X is 4 minus the amount of muscle drain you possess. If they do not, that enemy becomes a [Victim] and becomes [Vulnerable $C\times lvl$] to the next attack made against them by you.

\subsection*{Fourth \Facet\perk}
\textbf{Moment to Rest}: When you would use a surge from an ability outside of this track, you may instead lose one point of muscle drain.

\subsection*{Fifth \Facet\perk}
\textbf{Beg for my Freaking Forgiveness, Scum}: \emph{Enemies who have slighted you should be down on their knees, begging for your mercy.} When you use Angry Attack, you may also make a rider attack against that [Victim]. When you use Friendly Fury, the affected ally may make a rider attack against the chosen enemy. Either way, if the rider attack hits, that [Victim] becomes [Prone].

\subsection*{Sixth \Facet\perk}
\textbf{Reckless Abandon}: Once per round, when you take a major action that targets a [Victim], you may choose to gain a boost. If you do, you become [Vulnerable $C \times level$]. Once per round, when an ally who you have affected with Friendly Fury during your last turn takes a major action that targets a [Victim], that ally may choose to gain a boost. If they do, they become [Vulnerable $C \times level$].

\subsection*{Seventh \Facet\perk}
\textbf{You What, Mate?}: Whenever an enemy takes an action within 12 hexes of you, you may have that enemy become a [Victim] until the end of your next turn.
\end{multicols*}