\section{Brawler}
\textbf{Major Offensive}

Cause bodily harm to your enemies with your body, up close and personal.

\subsection*{Adaption}
This could be a form of martial arts, brawling, cybernetic enhancements, or raw animal fury.


\begin{multicols*}{2}
\subsection*{First \Facet\perk}
\textbf{One-Two} [WO]: Your unarmed attacks count as being armed with a melee weapon. As a major action, make two pool attacks dealing $10|13|17|20 \times Lvl$. \textbf{Boost}: Gain a +3 bonus to hit.

\textbf{Flying Tackle} [HO]: As a major action, dash up to your speed in a straight line and attack an adjacent opponent at the end of your movement with a +2 to hit. This deals $3\times C\times Lvl$ damage and you begin grappling them if you hit. If you moved at least 3 hexes with this action, that enemy becomes prone if you hit, and you inflict $2\times C\times Lvl$ to the target regardless of whether or not you hit. \textbf{Boost}: You deal an additional $\frac{3}{2} \times C\times Lvl$ damage if you hit.

\textbf{Jab} [W]: When you use a surge, make a single attack dealing $10|13|17|20 \times Lvl$ damage. This counts as a single attack with One-Two.

\subsection*{Second \Facet\perk}
\textbf{Give 'em the Chair!} [WO]: As a major action while wielding an improved weapon, make a single attack with a +1 to hit that deals $6 \times C \times Lvl$ and inflicts [Senseless; Stunned]. If you hit, the improvised weapon receives the same amount of damage, potentially destroying it.  \textbf{Boost}: Gain an additional +3 bonus to hit.

\textbf{Suplex} [O]: As a major action while grappling an opponent, you may cease grappling them. If you do, that enemy is moved into an adjacent unoccupied hex, becomes [Prone] and receives $4 \times C\times Lvl$ damage. \textbf{Boost}: Deal an additional $C\times Lvl$ damage.

\subsection*{Third \Facet\perk}
\textbf{Disorienting Blows}: One-Two and Give 'em the Chair inflict [Senseless; Off Balance].

\subsection*{Fourth \Facet\perk}
\textbf{Steel Grip}: The defense roll to escape your grapples has +2 potency.

\subsection*{Fifth \Facet\perk}
\textbf{Terrain Rip}: If you do not target a creature with One-Two and destroy a piece of [Destructible] terrain, you may instead begin wielding it as an improved weapon and immediately make an attack with Give 'em the Chair!

\subsection*{Sixth \Facet\perk}
\textbf{Throw}: Suplex may move the opponent to any unoccupied hex within range 3.

\subsection*{Seventh \Facet\perk}
\textbf{Concussion}: One-Two and Give 'em the Chair inflict [Blind 8] for the rest of the encounter. If you would attack a creature already affected by this ability, instead reduce the radius of this blinded effect by 1.

\end{multicols*}
